---
title: "RFA #40624 Equity Analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
params: 
  AppsThroughMonth: "2023-01-31"
  AppsCurrentMonth: "Jan 2023"
  Internal: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(kableExtra)
library(maps)
library(fontawesome)
library(flexdashboard)
library(leaflet)
library(tigris)
library(shiny)
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()


```

# Applications Awarded

## Row 

### Applications Awarded in **`r params$AppsCurrentMonth`** {.value-box}

```{r}
valueBox(5, 
  icon = "fa-check")

```

### Applications Awarded in **`r params$AppsCurrentMonth`** {.value-box}

```{r}
valueBox(5, 
  icon = "fa-check")

```

### Dollar Amount Awarded in **`r params$AppsCurrentMonth`** {.value-box}

```{r}
valueBox(scales::dollar(123456),
  icon = "fa-money-bill")
```

### Dollar Amount Awarded under HDG **`r params$AppsCurrentMonth`**  
```{r}
valueBox(scales::dollar((123456-25000)),
  icon = "fa-users")
```

### Dollar Amount Awarded under IMM **`r params$AppsCurrentMonth`**  
```{r}
valueBox(scales::dollar((25000)),
  icon = "fa-syringe")
```


## Row 

### Applications Awarded **to Date** {.value-box}

```{r}
valueBox(15, 
  icon = "fa-check-double")

```

### Applications Awarded **to Date** {.value-box}

```{r}
valueBox(15, 
  icon = "fa-check-double")

```

### Dollar Amount Awarded **to Date** {.value-box}

```{r}
valueBox(scales::dollar(1234567),
  icon = "fa-money-bill")
```

### Dollar Amount Awarded under HDG **to Date**  
```{r}
valueBox(scales::dollar((1234567-500000)),
  icon = "fa-users")
```


### Dollar Amount Awarded under IMM **to Date**  
```{r}
valueBox(scales::dollar((1234567-500000)),
  icon = "fa-syringe")
```

## Row

### Table 1

```{r}
mtcars |>
  select(mpg, cyl) |>
  group_by(cyl) |>
  summarise(AvgMPG = mean(mpg)) |>
  kbl() |>
  kable_styling(bootstrap_options = c("striped", "hover")) 
```

### Table 2

```{r}
mtcars |>
  select(mpg, cyl) |>
  group_by(cyl) |>
  summarise(AvgMPG = mean(mpg)) |>
  kbl() |>
  kable_styling(bootstrap_options = c("striped", "hover")) 
```

### Table 3

```{r}
mtcars |>
  select(mpg, cyl) |>
  group_by(cyl) |>
  summarise(AvgMPG = mean(mpg)) |>
  kbl() |>
  kable_styling(bootstrap_options = c("striped", "hover")) 
```

